---
title: "R Markdown: A Very Short Introduction"
# date: "..."
# author: "..."
output:
  pdf_document: 
    number_sections: true
---

# Exports to pdf and looks like LaTeX!

```{r include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE, 
  fig.align = "center",  
  out.width = '75%', 
  warning = FALSE, 
  message = FALSE
)
```

# R Markdown 

You can use R Markdown to

- save and execute code
- generate pdfs (like the lecture notes)
- generate html files (like the website for the lecture notes)
- make slides for presentations

Installation: follow the instruction on https://bookdown.org/yihui/rmarkdown/installation.html

Use ctrl + shift + k to knit your file (or click the Knit button in RStudio)

Some References:

1. R for Data Science: https://r4ds.had.co.nz/r-markdown.html

2. R Cookbook: https://rc2e.com/rmarkdown

3. R Markdown Cookbook: https://bookdown.org/yihui/rmarkdown-cookbook/

4. The files for generating the notes and assignments (onQ -> R Markdown Examples)

You may use R Markdown for your final project.

# Basic formatting

```
# Level 1 Heading
## Level 2 Heading
### Level 3 Heading
#### Level 4 Heading
##### Level 5 Heading
###### Level 6 Heading
```

## This is a subsection

### This is a subsubsection

## Formatting Text

* `*italics*` gives *italics*
* `**bold**` gives **bold**
*  `` `code` `` gives `code`      

See https://rc2e.com/rmarkdown#tab:commonMarkdown


## List

To create a bulleted list, start each line with an asterisk (*) like so:

```
* first item
* second item
* third item
```

Results:

* first item
* second item
* third item

To create a numbered list, start each line with 1. as follows:

```
1. first item
1. second item
1. third item
```

Results:

1. first item
1. second item
1. third item

```
1. first item
1. second item
   a. subitem 1
   a. subitem 2
      i. sub-subitem 1
      i. sub-subitem 2
   a. subitem 2
1. third item
```

Results:

1. first item
1. second item
   a. subitem 1
   a. subitem 2
      i. sub-subitem 1
      i. sub-subitem 2
   a. subitem 2
1. third item

## Table

```
||$H_0$ is true|$H_1$ is true|
|--|-----|----|
|Reject $H_0$| Type I error | No Error|
|Do not reject $H_0$| No Error | Type II Error|
```

Results:

||$H_0$ is true|$H_1$ is true|
|--|-----|----|
|Reject $H_0$| Type I error | No Error|
|Do not reject $H_0$| No Error | Type II Error|

# R code 

Two ways: inline and code chunk.

Code Chunk:

```{r}
x <- 6
sqrt(x)

sqrt(x)

sqrt(x)
```

Inline: The square root of `x` is `r sqrt(x)`. 

## Controlling Which Code and Results Are Shown

See: https://rc2e.com/rmarkdown#recipe-code-results

# Graphics

# Without echo = FALSE, the code will also come with the figure
```{r echo = FALSE}
library(ggplot2)
library(gcookbook)
ggplot(heightweight, aes(x = ageYear, y = heightIn, shape = sex, color = sex)) +
  geom_point()
```

# Latex Equation

R Markdown supports the LaTeX math equation notation.

Reference: https://en.wikibooks.org/wiki/LaTeX/Mathematics

Inline: $x + 2$

Displayed Equation:

\begin{equation*}
  \vec{v}_{MAX} = \argmax_{\vec{u} \in \mathbb{R}^{n}} 
  \bigg(S_{W}^{-1} S_B)
\end{equation*}

